Data for the Ontario Restaurant Closures Experiment

### 2021-02-18 outputs/paper/data_simulation.Rmd
merging .bibs, adding reminders to paper, and removing government funding

<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<CHECK IF THIS WORKS ONCE MINORITY DATA IS ADDED AMY>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
survey_2 <-
  bind_rows(
    survey_2 %>%
      filter(minority == "yes" & group == "treatment") %>%
      mutate(revenue = 0.88 * revenue)
    ,
    survey_2 %>%
      filter(minority == "no" & group == "treatment")
    ,
    survey_2 %>%
      filter(group == "control")
  )

@@

# Applications for government assistance
LORENA
## Survey 1
```{r}
survey_1 <- survey_1 %>%
  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD ASSISTANCE DATA SIMULATION HERE LORENA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
```

## Survey 2
```{r}
survey_2 <- survey_2 %>%
  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD ASSISTANCE DATA SIMULATION HERE LORENA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
```

>>>>

<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<CHECK IF THIS WORKS ONCE MINORITY DATA IS ADDED AMY>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
survey_2 <-
  bind_rows(
    survey_2 %>%
      filter((minority == "yes" | indigenous == "yes") & group == "treatment") %>%
      mutate(revenue = 0.88 * revenue)
    ,
    survey_2 %>%
      filter(minority == "no" & group == "treatment")
    ,
    survey_2 %>%
      filter(group == "control")
  )

@@
